ray

### 2022-03-20 outputs/paper/ray.Rmd
change labels

```{r}
income_data <- raw_data %>% select(c(hlthmntl, income16)) %>% filter(!is.na(income16), !is.na(hlthmntl)) %>%
  mutate(income = case_when(
    income16 <= 8 ~ "lowest",
    income16 <= 12 ~ "lower",
    income16 <= 17 ~ "lower middle",
    income16 <= 19 ~ "middle",
    income16 <= 21 ~ "upper middle",
    income16 > 21 ~ "upper",

@@

```{r}
first_born <- raw_data %>% select(c(hlthmntl, agekdbrn)) %>% filter(!is.na(agekdbrn), !is.na(hlthmntl)) %>%
  mutate(born = case_when(
    agekdbrn < 18 ~ '< 18',
    agekdbrn >= 18 & agekdbrn <= 29 ~ '18-29',
    agekdbrn >= 30 & agekdbrn <=39~ '30-39',
    agekdbrn >= 40 & agekdbrn <=49~ '40-49',
    agekdbrn >= 50 & agekdbrn <=64~ '50-64',
    agekdbrn >= 65 & agekdbrn <=89~ '65-89'

  )) %>%
  mutate(mntl_poor = case_when(1
    hlthmntl <= 3 ~ 'Good',
    hlthmntl >= 4 ~ 'Not Good',
  ))

>>>>

```{r}
income_data <- raw_data %>% select(c(hlthmntl, income16)) %>% filter(!is.na(income16), !is.na(hlthmntl)) %>%
  mutate(income = case_when(
    income16 <= 8 ~ "< $10,000",
    income16 <= 12 ~ "$10,000 - $20,000",
    income16 <= 17 ~ "$20,000 - $40,000",
    income16 <= 19 ~ "$40,000 - $60,000",
    income16 <= 21 ~ "$60,000 - $90,000",
    income16 > 21 ~ "> $90,000",

@@

```{r}
first_born <- raw_data %>% select(c(hlthmntl, agekdbrn)) %>% filter(!is.na(agekdbrn), !is.na(hlthmntl)) %>%
  mutate(born = case_when(
    agekdbrn < 18 ~ '< 18',
    agekdbrn >= 18 & agekdbrn <= 29 ~ '18-29',
    agekdbrn >= 30 & agekdbrn <=39~ '30-39',
    agekdbrn >= 40 & agekdbrn <=49~ '40-49',
    agekdbrn >= 50 & agekdbrn <=64~ '50-64',
    agekdbrn >= 65 & agekdbrn <=89~ '65-89'
  )) %>%
  mutate(mntl_poor = case_when(
    hlthmntl <= 3 ~ 'Good',
    hlthmntl >= 4 ~ 'Not Good',
  ))
